---
title: "Rock bbands"
author: "Kenny"
date: "Monday, January 26, 2015"
output: html_document
---

## codes to begin

> 1. deploy quantstrat  
> 2. suppress warnings   
> 3. remove objects from previous runnings
> 4. how does suppressWarnings() work


```{r}

require(quantstrat)
suppressWarnings(rm("order_book.bbands",pos=.strategy)) # to remove object from .strategy environment
suppressWarnings(rm("account.bbands","portfolio.bbands",pos=.blotter)) # to remove from .blotter environment
suppressWarnings(rm("account.st","portfolio.st","stock.str","stratBBands","initDate","initEq",'start_t','end_t')) # to remove from current environment

```

> inside `rm()`, argument `pos = .strategy` is strange to me, I need to **learn** more about it 

```
rm    (..., list = character(), pos = -1,
       envir = as.environment(pos), inherits = FALSE)
```
> **How to use args**:   
    1. ...  the objects to be removed, as names (unquoted) or character strings (quoted).  
    2. list a character vector naming objects to be removed.  
    3. pos where to do the removal. By default, uses the current environment. See ‘details’ for other possibilities.  

> **Diff between `pos` and `envir`**:   
    1. The `pos` argument can specify the environment from which to remove the objects in any of several ways:      
        - as an integer (the position in the search list);     
        - as the character string name of an element in the search list;      
        - or as an environment (including using sys.frame to access the currently active function calls).   
        - The envir argument is an alternative way to specify an environment, but is primarily there for back compatibility.    

## setup the string name of stocks to test

```{r}

stock.str='IBM' # string, name of stock
```


## setup some constants as parameters

```{r}

SD = 2 # how many standard deviations, traditionally 2
N = 20 # how many periods for the moving average, traditionally 20

```

## setup currency and stocks further

> 1. primary_id -- String describing the unique ID for the instrument. Most of the wrappers allow this to be a vector.

> 2. currency --  String describing the currency ID of an object of type currency

> 3. multiplier -- Numeric multiplier to apply to the price in the instrument to get to notional value.

```
currency(primary_id, identifiers = NULL, assign_i = TRUE, ...)

stock(primary_id, currency = NULL, multiplier = 1, tick_size = 0.01,
  identifiers = NULL, assign_i = TRUE, overwrite = TRUE, ...)
  
```

```{r}

currency('USD') # string

stock(stock.str,currency='USD',multiplier=1)

```

### later study

```

##### PLACE DEMO AND TEST DATES HERE #################
#
#if(isTRUE(options('in_test')$in_test))
#  # use test dates
#  {initDate="2011-01-01" 
#  endDate="2012-12-31"   
#  } else
#  # use demo defaults
#  {initDate="1999-12-31"
#  endDate=Sys.Date()}

```

### **why use = not  <-  here?**

## Setup initial data

```{r}

initDate='2006-12-31' # date is also a string
initEq=1000000

portfolio.st='bbands'  # it is a string, portfolio name in the strategy using strategy name
account.st='bbands' # same string

```

```{r}
# prepare the strings first
portfolio.st
stock.str
initDate

# with strings ready, now initialize the portfolio
initPortf(portfolio.st,symbols=stock.str, initDate=initDate)
```



## **initPortf()**

> **What is it?** -- Constructs and initializes **a portfolio object**, which is used to contain *transactions, positions, and aggregate level values*.

```
initPortf(name = "default", symbols, initPosQty = 0,
  initDate = "1950-01-01", currency = "USD", ...)
```

> **name** -- A name for the resulting portfolio object  
> **symbols** -- a list of instrument identifiers for those instruments contained in the portfolio
> **initPosQty** -- Initial position quantity, default is zero


## **initPortf() Details**

### Initializes a portfolio object, which is constructed from the following: 
> `$symbols`: the identifier used for each instrument contained in the portfolio. Use ls(Portfolio$symbols) to get a list of symbols.  

> `$symbols$[symbol]$txn`: irregular xts object of transactions data  

> `$symbols$[symbol]$posPL`: regular xts object of positions P&L calculated from transactions  

> `$symbols$[symbol]$posPL.ccy`: regular xts object of positions P&L converted to portfolio currency   

> `$summary`: aggregated portfolio values

### Each symbol has three associated tables. 

> 1. `txn`, is the transactions table, an irregular time series that contains information about trades or other position adjustments with the following columns:
    - `Txn.Qty`: the quantity, usually in units of contracts, changing hands. Positive values indicate a "buy" transaction; negative values are used to indicate a "sell."
    - `Txn.Price`: the price at which the transaction was made,
    - `Txn.Fees`: the sum total of transaction fees associated with the trade,
    - `Txn.Value`: the notional value of the transaction,
    - `Avg.Txn.Cost`: a calculated value for the average net price paid (received) per contract bought (received),
    - `Pos.Qty`: the resulting position quantity of contracts, calculated as the sum of the current transaction and the prior position,
    - `Pos.Avg.Cost`: the calculated average cost of the resulting position, and
    - `Realized.PL`: any prot or loss realized in the transaction from closing out a prior position

> 2. `posPL`, is a container used to store calculated P&L values from transactions and close prices within an instrument. The data series is, however, a regular time series. Columns of the table include:
    - `Pos.Qty` the quantity of the position held in the symbol,
    - `Pos.Value` the notional value of the position,
    - `Txn.Value` the net value of the transactions occuring,
    - `Txn.Fees` the total fees associated with transactions,
    - `Realized.PL` any net prot or loss realized through transactions,
    - `Unrealized.PL` any prot or loss associated with the remaining or open position, and
    - `Trading.PL` the sum of net realized and unrealized prot and loss.

> 3. `posPL.ccy`, is the same as the second but translated into the portfolio currency. For each portfolio, the summary slot contains a table that tracks calculated portfolio information through time. The table contains the following columns, held in a regular xts time series:
    - `Long.Value`: The sum of the notional value of all positions held long in the portfolio.
    - `Short.Value`: The sum of the notional value of all positions held short in the portfolio.
    - `Net.Value`: The sum of the notional long and notional short value of the portfolio.
    - `Gross.Value`: The sum of the notional long and absolute value of the notional short value of the portfolio.
    - `Txn.Fees`: The sum of brokerage commissions, exchange and other brokerage fees paid by the portfolio during the period.
    - `Realized.PL`: The sum of net realized prots or losses aggregated from the underlying positions in the portfolio. Gross realized prots can be calculated by adding Txn.Fees, the brokerage commission expenses for the period.
    - `Unrealized.PL`: The sum total increase or decrease in unrealized profits or losses on open positions in the portfolio at the end of the period.
    - `Net.Trading.PL`: Net realized prot or loss plus interest income plus change in unrealized prot or loss across all positions in the portfolio.

> TODO: add $account: name of the (one) affiliated account Outputs Initialized portfolio structure with a start date and initial positions.


## initAcct()

> **Output hidden** -- Outputs Constructs multi-column xts object used to **store aggregated portfolio calculations**

```
initAcct(name = "default", portfolios, initDate = "1950-01-01",
  initEq = 0, currency = "USD", ...)

```
> **name** -- Account name, as string  

> **portfolios** -- character vector of strings naming portfolios included in this account

```{r}

# initAcct(account.st,portfolios='bbands', initDate=initDate) same outcome as below

initAcct(account.st,portfolios= portfolio.st, initDate=initDate) 

```


### initAcct() NOTES 

> An **Account object** is a list of portfolios with portfolio summary information

> The Account object is modeled on the CFTC Thirteen-column presentation table.

> the first CFTC six column presentations: *Beg.Eq*, *Additions*, *Withdrawals*, *Net.Perf*, *End.Eq*, *Period.ROR*   

> note: No reason to persist *Period.ROR*, and *Beg.Eq* = Previous *End.Eq*, So we're left with four columns. Note that *Period.ROR* can be calc'd several different ways and is best left as a function.  

> the remaining 7 columns: - *Commission*, *Net.Realized*, *Interest*, *Ch.Unrealized*, *Advisory.Fees*, *Wealth.Index*   
  
> note: Again, no need to add *Wealth.Index*. Eventually, these additional columns will be useful. *Gross.Realized* will be calculated as (Net) `Realized.PL` + `Txn.Fees`  

> TODO Add `calcPeriodROR` function

> TODO Adddd functions `addCapital`, `drawCapital`, `addFees`

> initDate and initEq can be used in addCapital to initalize the account? Track cash at this level??? Calc gross PL and subtract fees? Or calc net PL and add fees.

```{r}

initOrders(portfolio=portfolio.st,initDate=initDate)
```

## **initOrders()**

> This function sets up the **order container** by portfolio.  

> Usage  `initOrders(portfolio = NULL, symbols = NULL, initDate = "1999-12-31", ...)`  

> Arguments  
      - `portfolio` text name of the portfolio to associate the order book with  
      - `symbols` a list of identifiers of the instruments to be contained in the Portfolio. The name of any associated price objects (xts prices, usually OHLC) should match these  
      - `initDate` date (ISO8601) prior to the first close price given in mktdata, used to initialize the order book with a dummy order  
      - `...` any other passthrough parameters  

> Details:   
      - If no symbols list is provided (the default) the function will attempt to retrieve the symbols list from the portfolio in the trade blotter.


```{r}

addPosLimit(portfolio.st, stock.str, initDate, 200, 2 ) #set max position, not sure what 2 = levels? mini position?
```

## `addPosLimit`

### purpose

> Many strategies will not be allowed to trade unconstrained. Typically, constraints will include position sizing limits.

### Usage

```
addPosLimit(portfolio, symbol, timestamp, maxpos, longlevels = 1,
  minpos = -maxpos, shortlevels = longlevels)

```

### Arguments

> `portfolio`  text name of the portfolio to place orders in

> `symbol`  identifier of the instrument to place orders for. The name of any associated price objects (xts prices, usually OHLC) should match these

> `timestamp` timestamp coercible to POSIXct that will be the time the order will be inserted on

> `maxpos`  numeric maximum long position for symbol

> `longlevels`  numeric number of levels

> `minpos`  numeric minimum position, default -minpos (short allowed use negative number)

> `shortlevels` numeric number of short levels, default longlevels

### Details

> `addPosLimit` works with `osMaxPos` to set and enforce **position sizing limits**.   
    
> 1. If levels=1, then all order sizing will be in the complete control of the strategy rules, up to the maximum position specified using addPosLimit's `maxpos` and `minpos` arguments.  

> 2. Simply setting a position limit will not do anything. The strategy entry rules also need to specify an the use of order sizing function `osMaxPos`, most typically as an argument to `ruleSignal`.  
    
> 3. `levels` are a simplification of more complex (proprietary) techniques sometimes used for order sizing. the max orderqty returned will be the limit/levels. Obviously the strategy rules could ask for smaller order sizes, but this is the default. **If you don't want to use levels, set them to 1**.  

> 4. It is also important to note that position limits may be time-varying.   
      
>   - If you only want one static maximum position limit, then call `addPosLimit` with a timestamp argument before your first trade.   

>   - If you want time varying limits, typically in response to some rebalancing rule or risk rule, set the `timestamp` at the time which you wish the limit to take effect.  



```{r}

stratBBands <- strategy("bbands")
stratBBands
```

## **`strategy()`** is about?

> `strategy()` is to create objects of type 'strategy'

> **What is for**:  
1. variables passed in `dots` will be added to the strategy object  
2. these variables may be used by **initialization and wrapup** functions  
3. they can also be used in **indicators, signals, and rules**.


```
strategy(name, ..., assets = NULL, constraints = NULL, store = FALSE)

```

> **Arguments**

> `name`  character string naming the strategy

> `...`   any other passthru parameters

> `assets`  optional list of assets to apply the strategy to, should normally be defined in the portfolio, not here

> `constraints`	  optional portfolio constraints object matching assets

> `store`   TRUE/FALSE whether to store the strategy in the .strategy environment, or return it. default FALSE

> also see `applyStrategy`


```{r}

#one indicator
stratBBands <- add.indicator(strategy = stratBBands, name = "BBands", arguments = list(HLC = quote(HLC(mktdata)), maType='SMA'), label='BBands') # arguments such as HLC and maType are both for function BBands, not for function add.indicator
stratBBands # check strategy content with the first indicator
```

## **`add.indicator`**  {quantstrat} 

> **purpose**     add an indicator to a strategy


```

add.indicator(strategy, name, arguments, parameters = NULL, label = NULL,
  ..., enabled = TRUE, indexnum = NULL, store = FALSE)
```

### **Arguments**

> `strategy`   an object (or the name of an object) type 'strategy' to add the indicator to

> `name`       name of the indicator function – must correspond to an R function

> `arguments`  default arguments to be passed to an indicator function when executed

> `parameters` vector of strings naming parameters to be saved for apply-time definition, default NULL, only needed if you need special names to avoid argument collision

> `label`      arbitrary text label for indicator output. This will also be used as the name of the indicator list when it is stored. NULL default will be converted to '<name>.ind'

> `...`        any other passthru parameters

> `enabled`    TRUE/FALSE whether the indicator is enabled for use in applying the strategy, default TRUE

> `indexnum`   if you are updating a specific indicator, the label or the index number in the $indicators list to update.

> `store`     TRUE/FALSE whether to store the strategy in the .strategy environment, or return it. default FALSE

### **Details**   

> **Indicators**    
-- are always `path-independent`, and should be constructed from *vectorized functions* where possible.

> **Indicators**   
- are applied before `signals` and `rules`, and *the output of indicators* may be used as inputs to construct signals or fire rules.

> **arguments and parameters**   
- are `named lists` that describe the arguments to be passed to the *indicator function*.  
- arguments is for defining any non-default arguments to be passed to the function named in the name of the indicator. For example, the *x argument to a moving average function* may be defined as x=quote(Cl(mktdata))

> **`quote()` and `mktdata`**    
- If you look at the demo scripts, you'll notice that we often use quote(mktdata) in *setting up indicators, signals, or rules*.  
- This tells R to *delay evaluation via quote()*, and to use the special variable `mktdata`.

> **`mktdata`**  
- is typically created internally to quantstrat by looking in the `global environment` for a time series of prices or returns.  
- `mktdata` may also contain other data you've manipulated outside quantstrat, though where possible you should use quantstrat to contain all the logic for the strategy, to aid in maintenance and modifications.

> **`quote()` and `mktdata' and delay**  
- The use of quote() tells R to not evaluate what's inside the quote until the function is evaluated later.   
- By the time that code is evaluated, mktdata will be populated with the correct price information based on the contents of whatever portfolio you are evaluating the strategy on.

> **`parameters`**  
- is another named list, and normally will not be needed.     
- If you have *multiple indicator, signal, or rule functions* share the that both *share the same argument names* and will need to *have different values passed to those arguments as defined parameters at apply-time*, then you may need to give them *unique names* so that delayed evaluation can sort it all out for you at apply-time.   
- We will endeavor to get an example of named parameters into the demo scripts.  

> **`label`**  
- if label is not supplied, NULL default will be converted to '<name>.ind'  
- unless there already exists an indicator with that label in which case it will be appended with a number (i.e. '<name>.ind.2', '<name>.ind.3', etc.)  
- If the indicator function returns *multiple columns*, the label will be paste'd to the end of either the returned column names or the respective column number when applying it to mktdata.

> see functions:  
- `quote`, `applyIndicators`, `add.signal`, `add.rule`

## **`BBands`**  {TTR}  

> **What is BBands**  
- Bollinger Bands are a way to compare a security's volatility and price levels over a period of time. Developed by John Bollinger.

```

BBands(HLC, n = 20, maType, sd = 2, ...)
```

### **`Arguments`**  

> **`HLC`**    
- Object that is coercible to xts or matrix and contains High-Low-Close prices. If only a univariate series is given, it will be used. See details.

> **`n`**  	
- Number of periods for moving average.

> **`maType`**    
- A function or a string naming the function to be called.

> **`sd`**    	
- The number of standard deviations to use.

> `...`    	
- Other arguments to be passed to the maType function.


### **Bollinger Bands consist of three lines**:

> **The middle band**  
- is generally a 20-period SMA of the typical price ([high + low + close]/3).   

> **The upper and lower bands**  
- are sd standard deviations (generally 2) above and below the MA.

> (not sure)   
- The middle band is usually calculated using the typical price, but if a univariate series (e.g. Close, Weighted Close, Median Price, etc.) is provided, it will be used instead.

### **returned Value**  

> A object of the same class as HLC or a matrix (if try.xts fails) containing the columns:  

> `dn` - The lower Bollinger Band.

> `mavg` - The middle Moving Average (see notes).

> `up` - The upper Bollinger Band.

> `pctB` - The %B calculation.

### **Note**

> Using any moving average other than `SMA` will result in **inconsistencies** between the moving average calculation and the standard deviation calculation. Since, by definition, a rolling standard deviation uses a simple moving average.

### **example**  

```{r}

## The examples below show the differences between using a
## High-Low-Close series, and just a close series when
## calculating Bollinger Bands.
data(ttrc)
bbands.HLC <- BBands( ttrc[,c("High","Low","Close")] )
head(bbands.HLC, 30)
bbands.close <- BBands( ttrc[,"Close"] )
head(bbands.close, 30)
```


```{r}

#add signals:
stratBBands <- add.signal(stratBBands,name="sigCrossover",arguments = list(columns=c("Close","up"),relationship="gt"),label="Cl.gt.UpperBand")
stratBBands # check strategy content with the first signal

stratBBands <- add.signal(stratBBands,name="sigCrossover",arguments = list(columns=c("Close","dn"),relationship="lt"),label="Cl.lt.LowerBand")
stratBBands # check strategy with the second signal

stratBBands <- add.signal(stratBBands,name="sigCrossover",arguments = list(columns=c("High","Low","mavg"),relationship="op"),label="Cross.Mid")
stratBBands # check strategy with the third signal

```
### **`add.signal`**  

> **`add.signal`**  
- add a signal to a strategy  
- adds a signal definition to a strategy object.

```

add.signal(strategy, name, arguments, parameters = NULL, label = NULL, ...,
  enabled = TRUE, indexnum = NULL, store = FALSE)

```


### **Arguments**  

> `strategy`    
- an object (or the name of an object) of type 'strategy' to add the signal to

> `name`  	
- name of the signal, must correspond to an R function

> `arguments`  	
- named list of default arguments to be passed to an signal function when executed

> `parameters`  	
- vector of strings naming parameters to be saved for apply-time definition,default NULL, only needed if you need special names to *avoid argument collision*  

> `label`  	
- arbitrary text label for signal output, default NULL

> '...'  	
- any other passthru parameters

> `enabled`  	
- TRUE/FALSE whether the signal is enabled for use in applying the strategy, default TRUE

> `indexnum`  	
- if you are *updating a specific signal*, the index number in the `$signals` list to update

> `store`  	
- TRUE/FALSE whether to store the strategy in the .strategy environment, or return it. default FALSE

### **Details**   

> `Signals`  
- denote times at which the strategy may want to take action.    
- Common signals types from the literature include `crossovers`, `thresholds`, or *other interactions* between your `mktdata` and your indicators.  

> `label` for names
- if label is not supplied, NULL default will be converted to '<name>.sig'  
- if the signal function returns one named column, we use that, and ignore the label  
- If the signal function returns multiple columns, the label will be paste'd to either the returned column names or the respective column number.  

### returned Value  

> **(not sure)** if strategy was the name of a strategy, the name. If it was a strategy, the updated strategy.  

> See Also  
- `applySignals` `add.indicator` `add.rule` `sigComparison` `sigCrossover` `sigFormula` `sigPeak` `sigThreshold`  


## **`sigCrossover`**  

### **what `sigCrossover` is for**  
- generate a crossover signal  
- This will generate a crossover signal, which is a dimension-reduced version of a comparison signal sigComparison.  

```

sigCrossover(label, data = mktdata, columns, relationship = c("gt", "lt",
  "eq", "gte", "lte"), offset1 = 0, offset2 = 0)

```
### **how to apply `sigCrossover` into `add.signal`?**  

> `sigCrossover` arguments
- arguments like `label` and `data` can be ignored in `add.signal`  
- `label=label` in `add.signal` and `data = mktdata` are taken for granted


### **Arguments**  

> `label`    
- text label to apply to the output

> `data`  
- data to apply crossover to

> `columns`  	
- named columns to apply crossover of the first against the second

> `relationship`  	
- one of c("gt","lt","eq","gte","lte") or reasonable alternatives

> `offset1`  	(not sure)  
- numeric offset to be added to the first column prior to comparison

> `offset2`  	(not sure)  
- numeric offset to be added to the second column prior to comparison

### **Details**  

> It will return TRUE on the period in which there is a crossover in the direction specified by relationship, and NA otherwise.

> If you want all the information, use a comparison instead. `op` = opposite


# lets add some rules
stratBBands <- add.rule(stratBBands,name='ruleSignal', arguments = list(sigcol="Cl.gt.UpperBand",sigval=TRUE, orderqty=-100, ordertype='market', orderside=NULL, threshold=NULL,osFUN=osMaxPos),type='enter')
stratBBands <- add.rule(stratBBands,name='ruleSignal', arguments = list(sigcol="Cl.lt.LowerBand",sigval=TRUE, orderqty= 100, ordertype='market', orderside=NULL, threshold=NULL,osFUN=osMaxPos),type='enter')
stratBBands <- add.rule(stratBBands,name='ruleSignal', arguments = list(sigcol="Cross.Mid",sigval=TRUE, orderqty= 'all', ordertype='market', orderside=NULL, threshold=NULL,osFUN=osMaxPos),type='exit')

#alternately, to exit at the opposite band, the rules would be...
#stratBBands <- add.rule(stratBBands,name='ruleSignal', arguments = list(data=quote(mktdata),sigcol="Lo.gt.UpperBand",sigval=TRUE, orderqty= 'all', ordertype='market', orderside=NULL, threshold=NULL),type='exit')
#stratBBands <- add.rule(stratBBands,name='ruleSignal', arguments = list(data=quote(mktdata),sigcol="Hi.lt.LowerBand",sigval=TRUE, orderqty= 'all', ordertype='market', orderside=NULL, threshold=NULL),type='exit')

#TODO add thresholds and stop-entry and stop-exit handling to test

getSymbols(stock.str,from=initDate,index.class=c('POSIXt','POSIXct'))
start_t<-Sys.time()
out<-try(applyStrategy(strategy=stratBBands , portfolios='bbands',parameters=list(sd=SD,n=N)) )

# look at the order book
#getOrderBook('bbands')
end_t<-Sys.time()
print("strat execution time:")
print(end_t-start_t)

start_t<-Sys.time()
updatePortf(Portfolio='bbands',Dates=paste('::',as.Date(Sys.time()),sep=''))
end_t<-Sys.time()
print("updatePortf execution time:")
print(end_t-start_t)

chart.Posn(Portfolio='bbands',Symbol=stock.str)
plot(add_BBands(on=1,sd=SD,n=N))


###############################################################################
# R (http://r-project.org/) Quantitative Strategy Model Framework
#
# Copyright (c) 2009-2012
# Peter Carl, Dirk Eddelbuettel, Brian G. Peterson, Jeffrey Ryan, and Joshua Ulrich 
#
# This library is distributed under the terms of the GNU Public License (GPL)
# for full details see the file COPYING
#
# $Id$
#
###############################################################################

##### PLACE THIS BLOCK AT END OF DEMO SCRIPT ################### 
# book  = getOrderBook(port)
# stats = tradeStats(port)
# rets  = PortfReturns(acct)
################################################################

```